COG-ED Manuscript

### 2022-06-13 06_Paper/COG-ED/Manuscript.Rmd
changed MLM description

To determine the influence of task performance on the association of SVs and *n*-back level, we will perform MLM. 
We will apply restricted maximum likelihood (REML) to fit the model.
As an effect size measure for random effects we will firstly calculate the intraclass correlation (ICC), which displays the proportion of variance that is explained by differences between persons.
Second, we will estimate a random slopes model of n-back level (level 1, fixed and random factor: 0-back, 1-back, 2-back, 3-back) predicting SV nested within subjects.
As Mussel et al.[-@Mussel2016] could show, participants with high versus low NFC not only have a more shallow decline in performance with higher n-back levels, but show a demand-specific increase in EEG theta oscillations, which has been associated with mental effort.
We control for performance, i.e., *d'* (level 1, fixed factor, continuous), median RT (level 1, fixed factor, continuous) in order to eliminate a possible influence of declining performance on SV ratings.
$$
SV \sim level\ + d' + median RT + (level|subject)
$$
Level-1-predictors will be centered within cluster as recommended by Enders & Tofighi[-@Enders2007]. 
By this, the model yields interpretable parameter estimates. 
If necessary, we will adjusted the optimization algorithm to improve model fit. 
We will visually inspect the residuals of the model for evidence to perform model criticism. 
This will be done by excluding all data points with absolute standardized residuals above 3 SD. 
As effect size measures, we will calculate pseudo *R²* for our model and *f²* to estimate the effect of n-back level according to Lorah[-@Lorah2018].
To ensure the validity of the MLM, we will conduct a specification curve analysis[@Simonsohn2020], which will include 63 possible preprocessing pipelines of the RT data.
These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, 2, 2.5, or 3\ $MAD$ from the median, RTs below 100\ or\ 200\ ms), and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within *n*-back levels).
The MLM will be run with each of the 63\ pipelines, which will also include our main pipeline (untransformed data, exclusion of RTs below 100\ ms).
The ratio of pipelines that lead to significant versus non-significant effects will provide an indication of how robust the effect actually is.

>>>>

To determine the influence of task performance on the association of SVs and *n*-back level, we will perform MLM. 
We will apply restricted maximum likelihood (REML) to fit the model.
As an effect size measure for random effects we will firstly calculate the intraclass correlation (ICC), which displays the proportion of variance that is explained by differences between persons.
Second, we will estimate a random slopes model of n-back level (level 1, fixed and random factor: 1-back, 2-back, 3-back, 4-back) predicting SV nested within subjects.
As Mussel et al.[-@Mussel2016] could show, participants with high versus low NFC not only have a more shallow decline in performance with higher n-back levels, but show a demand-specific increase in EEG theta oscillations, which has been associated with mental effort.
We control for performance, i.e., *d'* (level 1, fixed factor, continuous), median RT (level 1, fixed factor, continuous) in order to eliminate a possible influence of declining performance on SV ratings.
$$
SV \sim level\ + d' + median RT + (level|subject)
$$
Level-1-predictors will be centered within cluster as recommended by Enders & Tofighi[-@Enders2007]. 
By this, the model yields interpretable parameter estimates. 
If necessary, we will adjusted the optimization algorithm to improve model fit. 
We will visually inspect the residuals of the model for evidence to perform model criticism. 
This will be done by excluding all data points with absolute standardized residuals above 3 SD. 
As effect size measures, we will calculate pseudo *R²* for our model and *f²* to estimate the effect of n-back level according to Lorah[-@Lorah2018].
To ensure the validity of the MLM, we will conduct a specification curve analysis[@Simonsohn2020], which will include 63 possible preprocessing pipelines of the RT data.
These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, 2, 2.5, or 3\ $MAD$ from the median, RTs below 100\ or\ 200\ ms), and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within *n*-back levels).
The MLM will be run with each of the 63\ pipelines, which will also include our main pipeline (untransformed data, exclusion of RTs below 100\ ms).
The ratio of pipelines that lead to significant versus non-significant effects will provide an indication of how robust the effect actually is.
